Manuscript draft

### 2019-08-27 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

@@

Our findings support a lot of previous work that has been done, but we are doing this with a much larger and more comprehensive dataset, with better standardisation of available data.

>>>>

Many of our findings support and clarify previously published work; however we use a much larger and more comprehensive database than has previously been available, allowing for higher quality control and standardisation of data. This enalbed us to control for factors not previously controlled for - such as stand age, methodology, flux components, and disturbance regime - to gain a stronger understanding of latitudinal and climatic effects on productivity.

Despite the high standard of data quality in the ForC database, there are still significant limitations on our analyses. We standardised methodologies as far as possible, ensuring that there was consistency in the components included for each carbon flux. However, field techniques for estimating components of primary productivity are variable in their accuracy. This is particularly true for measures of BNPP, which are often estimated by extrapolating measures of ANPP. Even where BNPP is calculated through direct soil sampling, measures are often taken to insufficient depth, leading to underestimation of the flux. It is challenging to account for this type of variability in quality of field data, and our analyses largely assume good faith in data quality. While we have strong confidence in our analyses of well-understood fluxes, such as GPP, ANPP, and ANPP~woody stem~, we recommend caution in drawing firm conclusions from our analyses of BNPP, BNPP~fine root~, and, to some extent, NPP. We expect that, as field techniques improve the accuracy of estimates of these fluxes in the future, our understanding of the relationship of BNPP with climate variables will change. It is possible that the low R^2^ values for BNPP that we find are a result of lower accuracy in field measures of these fluxes.

@@
